Your Title Here

### 2025-05-08 latex/draft.tex
更新论文

Bibliometrics, which employs quantitative methods to analyze research trends and knowledge structures across disciplines, has become pivotal in mapping technological innovations like drone applications. A seminal study by Fayyad et al. (2025) A Scientometric Analysis of Drone-Based Structural Health Monitoring and New Technologies identifies four research clusters in drone-enabled infrastructure monitoring, emphasizing AI integration and automation gaps while projecting breakthroughs in digital twins and robotics. Rejeb et al. (2022) in Drones in Agriculture: A Review and Bibliometric Analysis reveal dominant themes like precision farming and IoT integration, highlighting remote sensing and deep learning as key drivers reshaping agricultural efficiency. Similarly, Iqbal et al. (2023) in Drones for Flood Monitoring, Mapping and Detection map global research trajectories through bibliometric networks, stressing computer vision and real-time data fusion as critical for enhancing disaster response frameworks. For forestry applications, da Silva et al. (2024) in Using Drones for Dendrometric Estimations demonstrate UAVs' superiority over traditional methods in measuring tree height and biomass, with RGB sensors emerging as the primary tool for cost-effective forest management. These studies collectively underscore bibliometrics' role in crystallizing interdisciplinary advancements, identifying implementation barriers (e.g., regulatory fragmentation in healthcare logistics), and prioritizing future research directions like sustainable multimodal integration and AI-driven scalability.

\section{Methods}
This section describes the methods used

>>>>

Bibliometrics, a quantitative research method that employs statistical and computational techniques to analyze publication patterns, citation networks, and knowledge evolution within academic domains, serves as a critical tool for mapping interdisciplinary advancements and identifying emerging trends. Its significance lies in synthesizing fragmented research landscapes, revealing collaborative networks, and prioritizing future directions through metrics such as co-citation analysis, keyword clustering, and temporal trend mapping (\cite{WOS:000958189000001}). Within drone technology research, several studies demonstrate the application of bibliometric approaches to map interdisciplinary knowledge domains. For instance, Fayyad et al.   (\cite{WOS:001229751500001}) utilize scientometric analysis to categorize drone-based structural health monitoring (SHM) into four research clusters.  Rejeb et al. (\cite{WOS:000830895100002})) identify remote sensing, precision agriculture, and IoT as dominant themes in agricultural drone studies, while co-citation analysis reveals six research clusters. Iqbal et al.  (\cite{WOS:000914960100001})) highlight evolving priorities in drones for flood management, emphasizing computer vision and real-time detection systems.  Da Silva et al.  (\cite{WOS:001366904300001})) employ bibliometrics to reveal that UAVs are increasingly used over traditional forest inventories to efficiently assess variables like tree height, DBH, biomass, and canopy area through high-resolution sensors. While prior bibliometric reviews like "Analyzing Forklift and Drone Applications in Sustainable Logistics" (\cite{WOS:001329532200078})) provide initial insights into drone logistics, their broad scope—spanning both forklifts and drones—and exclusive focus on sustainability limit granular analysis of drone-specific logistics. In addition, this study remains confined to quantitative metrics, without in-depth review of the literature. It also relies on keyword-based search on data collection, which can be improved by manual screening of the search results. Our study addresses these gaps through a dedicated drone logistics bibliometric analysis, combining quantitative bibliometrics with qualitative analysis of domain-specific innovations.

The primary objective of this bibliometric study is to systematically map and evaluate the intellectual landscape of drone logistics research, focusing on its evolution, thematic priorities, and collaborative networks. To address this aim, the analysis integrates performance metrics (publication trends, citation impact, leading countries/institutions, prominent journals, and dominant Web of Science categories) with science mapping techniques (keyword co-occurrence, co-authorship networks, bibliographic coupling, and citation dynamics) using data extracted from Scopus and Web of Science. Central research questions include:

(1) Identification of seminal publications and key contributors shaping the foundation of drone logistics research​.
(2) Semantic clustering of research streams and thematic evolution in the field of drone logistics.
(3) Temporal dynamics of collaboration networks and emerging frontiers​ in drone logistics research​.

The paper is structured as follows: The methods section​​ details the data collection protocol, including database selection, search queries, inclusion/exclusion criteria, and analytical tools. The results section​​ presents bibliometric outputs: temporal publication trends, leading contributing countries, high-impact journals, and keyword co-occurrence clusters. ​​The discussions​ section integrates these metrics with a qualitative synthesis of key literature, categorizing the field into subdomains and evaluating their interconnections, gaps, and evolution over time. The conclusions section​​ summarizes the findings of the study, acknowledges limitations and proposes future research directions.

\section{Methods}
\subsection{Data Collection} 
这是数据收集部分的详细内容...
